---
title: "Indicator 3 - Amount of posture changes by time unit"
author: "Mathilda Alhamadah"
date: "2025-06-18"
output:
  html_document:
    toc: true             #table des matières
    toc_float: true       #table des matières toujours visible
    theme: bootstrap      #changer le thème de la page
    highlight: zenburn    #changer le thème des chunks
    
editor_options: 
  markdown: 
    wrap: 80
---

```{r}
load("data_only_8h_21h_from_04_07_2022_to_06_07_2022.Rdata")
```

## 1.3 Amount of posture changes by time unit

### 1.3.1 Function

posture_no_na is a temporary variable : every not_visible & NA posture will be
replaced by the previous one. Useful only to count the amount of posture
changes.

```{r}
# Function 1 : Detect time changes

amount_posture_changes <- function(
    data,
    group_time){ #group_time : "number + unit" (among : second, minute, hour, day,                     week, month, bimonth, quarter, season, halfyear and year)
  
  # Temporary variable : not_visible & NAs replaced by NAs
  data <- data %>% 
    mutate(posture_no_NA = case_when(
      name == "not visible" ~ NA,  #NA if not visible
      is.na(name) ~ NA,            #NA if NA
      TRUE ~ name)                 #else : posture name
      )  
  
  data <- data %>%
    fill(posture_no_NA)
  
  # variable posture_no_NA : mettre les not visible en NA et laisser les NA en NA
  # puis remplir les NA à l'aide de la dernière valeur
  
  
  # Detect position changes
  data_valid <- data %>%
    arrange(Date_Time) %>%  #Sort by date
    # Movement : if posture != posture at previous time (skip NAs & not_visible)
    mutate(Position_change = posture_no_NA != lag(posture_no_NA, default = first(posture_no_NA)))

  # Results
  return(changes_by_group_time(data_valid, time_gap = group_time))
  }



# Function 2 : Get the sum of posture changes by time unit

changes_by_group_time <- function(data, time_gap) {
  data %>%
    mutate(Time_group = floor_date(Date_Time, unit = time_gap)) %>% #make time groups
    group_by(Time_group) %>%
    summarise(Nb_changes = sum(Position_change, na.rm = TRUE)) %>% #sum changes
    ungroup()                                     #just in case
}

```

```{r}
# Changes per 15minutes & per day
amount_changes_data_8h_21h_04_to_06_07_2022 <- amount_posture_changes(data_8h_21h_04_to_06_07_2022, "15 minute")

amount_posture_changes(data_8h_21h_04_to_06_07_2022, "1 day")
```

### 1.3.2 Chart : Skip parts between 21h and 8h

```{r}
  # Add a new time variable to replace the real time

add_compressed_time_variable <- function(data) {
  data$compressed_time <- seq_len(nrow(data))-1
  return(data)
}
```

```{r}
 # Dataset

amount_changes_data_8h_21h_04_to_06_07_2022_compressed_time <- add_compressed_time_variable(amount_changes_data_8h_21h_04_to_06_07_2022)
```

```{r}
  # Areas to color

#red : no data available (corrupted videos)
#

areas <- data.frame(
  xmin = c(0, 43, 96,
           11, 21, 53, 109,
           36, 57, 113,
           15),
  xmax = c(11, 53, 109,
           15, 28, 57, 113,
           43, 62, 124,
           21),
  fill = c("No data", "No data", "No data",
           "Inactive", "Inactive", "Inactive", "Inactive",
           "Active", "Active", "Active",
           "Out for implant")
)



  # Plot

ggplot(amount_changes_data_8h_21h_04_to_06_07_2022_compressed_time,
       aes(x = compressed_time, y = Nb_changes)) +
  
  geom_rect(data = areas, aes(xmin = xmin, xmax = xmax, ymin = -Inf, ymax = Inf, fill = fill),
            inherit.aes = FALSE, alpha = 0.2) +
  
  geom_line() +
  #xlab("Temps entre 8h et 21h chaque jour") +
  ylab("Nombre de changements de position") +
  ggtitle("Changements de position du renard 4313", subtitle = "Du 4 au 6 juillet 2022, toutes les 15 minutes") +
  scale_x_continuous(name = "Temps entre 8h et 21h chaque jour",
                     breaks = c(0,10,20,30,40,50,60,70,80,90,100,110,120,130,140,150))
```

Spike between 28&36 : because the fox is waking up from anesthesia & he's trying
to get up, but it doesn't work well. So a lot of alternates between lying &
sitting.

```{r}
test2 <- data_8h_21h_04_to_06_07_2022[data_8h_21h_04_to_06_07_2022$Date_Time > as.POSIXct("2022-07-04 11:50:00")
                             & data_8h_21h_04_to_06_07_2022$Date_Time < as.POSIXct("2022-07-04 12:05:00") ,  ]
```
