---
title: "Indicator 2 - Movement score, posture quantification"
author: "Mathilda Alhamadah"
date: "2025-06-18"
output:
  html_document:
    toc: true             #table des matières
    toc_float: true       #table des matières toujours visible
    theme: bootstrap      #changer le thème de la page
    highlight: zenburn    #changer le thème des chunks
    
editor_options: 
  markdown: 
    wrap: 80
---

```{r}
library(jsonlite)
library(purrr)
library(curl)
library(dplyr)
library(lubridate)
library(tidyr)
library(ggplot2)
library(patchwork)
```

```{r}
load("reliable_data_8h_21h_05_07_to_08_08_2022.Rdata")
```

# Movement score : quantify each posture & sum it

What we do have : 0 = lying, 1 = standing, 2 = sitting.

What we want : 0 = lying, 1= sitting, 2= standing (so that NA is only for missing
data & fox not visible). What we did is equevalent of multiplying the proportion
of time spent in a posture by the index of this posture (1 2 or 3), but with a removal of NA values.

## 1. Function

```{r}
#Change posture code to lying-sitting-standing (instead of lying-standing-sitting)
posture_123 <- function(data){
  data <- data %>% 
  mutate(increasing_code = case_when(name=="lying" ~ 0,
                                   name=="sitting" ~ 1,
                                   name=="standing" ~ 2,
                                   name=="not visible" ~ NA, #to avoid having it in the sum
                                   TRUE ~ NA))
}
```

```{r}
# Amount activity function
amount_activity <- function(data, interval_seconds) {
  data <- data %>% arrange(Date_Time)
  
  start_time <- min(data$Date_Time)
  end_time <- max(data$Date_Time)
  
  intervals <- seq(from = start_time, to = end_time, by = interval_seconds)
  
  df_counts <- data.frame(
    interval_start = intervals[-length(intervals)],
    interval_end = intervals[-1]
  )
  
  df_counts <- df_counts %>%
    rowwise() %>%
    mutate(
      # Filtrer les valeurs non-NA pour le calcul de total_activity
      valid_values = list(data$increasing_code[data$Date_Time >= interval_start & data$Date_Time < interval_end & !is.na(data$increasing_code)]),
      total_activity = sum(valid_values,
                           na.rm = FALSE) / 2, # Diviser par 2 pour obtenir un max de 1. Normalement pas de NA
      # Calculer le nombre de valeurs non-NA
      no_na_count = length(valid_values),
      # Calculer activity_proportion en fonction du nombre de valeurs non-NA
        # To do later : add a filter so that if too many NAs the proportion is not computed ? 
      activity_proportion = ifelse(no_na_count > 0, total_activity / no_na_count, NA)
    ) %>%
    select(-valid_values, -no_na_count) # Supprimer les colonnes temporaires
  
  return(df_counts)
}

```


```{r}
# Function to remove the 21h-8h gap that has been re-created by the amount_activity function
filter_8h_21h <- function(data, time_column){
  data <- data %>% 
    filter(hour({{time_column}}) >= 8 & hour({{time_column}}) < 21)
  return(data)
}
```

## 2. Chronologic series

```{r function_add_comressed_time_variable}
# Useful to skip the 21h-8h gap when plotting/ analyzing
add_compressed_time_variable <- function(data) {
  data$compressed_time <- seq_len(nrow(data))-1 #-1 to make it start with 0
  return(data)
}
```

```{r}
plot_activity_with_areas <- function(data, nb_min, areas,
                                     title, subtitle,
                                     x_lab, y_lab) {

  # Create the plot
  ggplot(data, aes(x = compressed_time, y = activity_proportion)) +
    geom_line() +
    ylab(y_lab) +
    ggtitle(title,
            subtitle = paste(subtitle, "every", nb_min, "minutes."))
}

```

Do everything in 1 chunk from data to plot :
```{r}
from_data_to_plot <- function(data_8h_21h,
                              interval_seconds,
                              time_column = interval_start,
                              title,
                              subtitle,
                              x_lab,
                              y_lab){
  
  data_8h_21h_increasing_code <- posture_123(data_8h_21h)

  amount_activity_data <- amount_activity(data = data_8h_21h_increasing_code,
                                     interval_seconds = interval_seconds) # default = 900 seconds (15 minutes)

# remove the 21h-8h gap
  amount_activity_8h_21h <- filter_8h_21h(
    data = amount_activity_data,
    time_column = interval_start)

# remove inexistant data
  amount_activity_8h_21h <- amount_activity_8h_21h %>%
    filter(interval_start < "2022-07-15 00:00:00" | interval_start >= "2022-08-03 00:00:00")


  # Compressed time variable to skip parts between 21h and 8h
  amount_activity_x_minutes_8h_21h_compressed_time <- add_compressed_time_variable(amount_activity_8h_21h)

  plot <- plot_activity_with_areas(
    amount_activity_x_minutes_8h_21h_compressed_time,
    nb_min = interval_seconds/60,
    areas = areas,
    title = title,
    subtitle = subtitle,
    x_lab = x_lab,
    y_lab = y_lab)
  
  return(plot)

  }
```

```{r}
from_data_to_plot(data_8h_21h = reliable_data_8h_21h_05_07_to_08_08_2022,
                  interval_seconds = 900,
                  title = "Activity score for fox 4313",
                  subtitle = "From 05/07 to 08/08, year 2022",
                  x_lab = "Time between 8h and 21h each day",
                  y_lab = "Movement score by summing posture indices")
```


