---
title: "Indicator 2 - Movement score, posture quantification"
author: "Mathilda Alhamadah"
date: "2025-06-18"
output:
  html_document:
    toc: true             #table des matières
    toc_float: true       #table des matières toujours visible
    theme: bootstrap      #changer le thème de la page
    highlight: zenburn    #changer le thème des chunks
    
editor_options: 
  markdown: 
    wrap: 80
---

```{r}
library(jsonlite)
library(purrr)
library(curl)
library(dplyr)
library(lubridate)
library(tidyr)
library(ggplot2)
library(patchwork)
```

```{r}
load("data_8h_21h_04_to_14_07_2022.Rdata")
```

# Movement score : quantify each posture & sum it

What we do have : 0 = lying, 1 = standing, 2 = sitting.

What we want : 1 = lying, 2= sitting, 3= standing (so that 0 is only for missing
data & fox not visible). What we did is equevalent of multiplying the proportion
of time spent in a posture by the index of this posture (1 2 or 3).

## 1. Function

```{r}
#Change posture code to lying-sitting-standing (instead of lying-standing-sitting)
posture_123 <- function(data){
  data <- data %>% 
  mutate(increasing_code = case_when(name=="lying" ~ 0,
                                   name=="sitting" ~ 1,
                                   name=="standing" ~ 2,
                                   name=="not visible" ~ NA, #to avoid having it in the sum
                                   TRUE ~ NA))
}
```

```{r}
# Amount activity function
amount_activity <- function(data, interval_seconds) {
  data <- data %>% arrange(Date_Time)
  
  start_time <- min(data$Date_Time)
  end_time <- max(data$Date_Time)
  
  intervals <- seq(from = start_time, to = end_time, by = interval_seconds)
  
  df_counts <- data.frame(
    interval_start = intervals[-length(intervals)],
    interval_end = intervals[-1]
  )
  
  df_counts <- df_counts %>%
    rowwise() %>%
    mutate(
      total_activity =
        sum(data$increasing_code[data$Date_Time >= interval_start
                                 & data$Date_Time < interval_end],
            na.rm = TRUE)/2, #divide by 2 because max score = 2 : get a max to 1
      activity_proportion = ifelse(
        total_activity != 0,
        (total_activity) / nrow(data[data$Date_Time >= interval_start & data$Date_Time < interval_end, ]), #divided by 2 because score max = 2
        0
      )
    )
  
  return(df_counts)
}
```

```{r}
# test2

amount_activity <- function(data, interval_seconds) {
  data <- data %>% arrange(Date_Time)
  
  start_time <- min(data$Date_Time)
  end_time <- max(data$Date_Time)
  
  intervals <- seq(from = start_time, to = end_time, by = interval_seconds)
  
  df_counts <- data.frame(
    interval_start = intervals[-length(intervals)],
    interval_end = intervals[-1]
  )
  
  df_counts <- df_counts %>%
    rowwise() %>%
    mutate(
      # Filtrer les valeurs non-NA pour le calcul de total_activity
      valid_values = data$increasing_code[data$Date_Time >= interval_start & data$Date_Time < interval_end & !is.na(data$increasing_code)],
      total_activity = sum(valid_values, na.rm = TRUE) / 2, # Diviser par 2 pour obtenir un max de 1
      # Calculer le nombre de valeurs non-NA
      non_na_count = sum(!is.na(data$increasing_code[data$Date_Time >= interval_start & data$Date_Time < interval_end])),
      # Calculer activity_proportion en fonction du nombre de valeurs non-NA
      activity_proportion = ifelse(non_na_count > 0, total_activity / non_na_count, NA)
    ) %>%
    select(-valid_values, -non_na_count) # Supprimer les colonnes temporaires
  
  return(df_counts)
}

```

```{r}
# test 3
amount_activity <- function(data, interval_seconds) {
  data <- data %>% arrange(Date_Time)
  
  start_time <- min(data$Date_Time)
  end_time <- max(data$Date_Time)
  
  intervals <- seq(from = start_time, to = end_time, by = interval_seconds)
  
  df_counts <- data.frame(
    interval_start = intervals[-length(intervals)],
    interval_end = intervals[-1]
  )
  
  df_counts <- df_counts %>%
    rowwise() %>%
    mutate(
      # Filtrer les valeurs non-NA pour le calcul de total_activity
      valid_values = list(data$increasing_code[data$Date_Time >= interval_start & data$Date_Time < interval_end & !is.na(data$increasing_code)]),
      total_activity = sum(valid_values,
                           na.rm = FALSE) / 2, # Diviser par 2 pour obtenir un max de 1. Normalement pas de NA
      # Calculer le nombre de valeurs non-NA
      no_na_count = length(valid_values),
      # Calculer activity_proportion en fonction du nombre de valeurs non-NA
      activity_proportion = ifelse(no_na_count > 0, total_activity / no_na_count, NA)
    ) %>%
    select(-valid_values, -no_na_count) # Supprimer les colonnes temporaires
  
  return(df_counts)
}

```

```{r}
#test amount_activity

data_8h_21h_04_to_14_07_2022 <- posture_123(data_8h_21h_04_to_14_07_2022)

amount_activity(data_8h_21h_04_to_14_07_2022)

datatest <- data_8h_21h_04_to_14_07_2022 %>% arrange(Date_Time)

#interval_seconds <- 900
  
  start_time <- min(datatest$Date_Time)
  end_time <- max(datatest$Date_Time)
  
  intervals <- seq(from = start_time, to = end_time, by = interval_seconds)
  
  df_counts <- data.frame(
    interval_start = intervals[-length(intervals)], #enlever le dernier
    interval_end = intervals[-1]                    #enlever le premier
  )
  
  df_counts <- df_counts %>%
    rowwise() %>%
    mutate(
      # Filtrer les valeurs non-NA pour le calcul de total_activity
      valid_values = list(datatest$increasing_code[datatest$Date_Time >= interval_start & datatest$Date_Time < interval_end & !is.na(datatest$increasing_code)]),
      total_activity = sum(valid_values,
                           na.rm = FALSE) / 2, # Diviser par 2 pour obtenir un max de 1. Normalement pas de NA
      # Calculer le nombre de valeurs non-NA
      no_na_count = length(valid_values),
      # Calculer activity_proportion en fonction du nombre de valeurs non-NA
      activity_proportion = ifelse(no_na_count > 0, total_activity / no_na_count, NA)
    ) %>%
    select(-valid_values, -no_na_count) # Supprimer les colonnes temporaires
  
```


```{r}
# Function to remove the 21h-8h gap that has been re-created by the amount_activity function
filter_8h_21h <- function(data, time_column){
  data <- data %>% 
    filter(hour({{time_column}}) >= 8 & hour({{time_column}}) < 21)
  return(data)
}
```

## 2. Chronologic series

```{r function_add_comressed_time_variable}
# Useful to skip the 21h-8h gap when plotting/ analyzing
add_compressed_time_variable <- function(data) {
  data$compressed_time <- seq_len(nrow(data))-1 #-1 to make it start with 0
  return(data)
}
```

```{r}
get_areas_color <- function(data, times_vector_xmin, times_vector_xmax, fill) {
  # S'assurer que le vecteur de temps est au format POSIXct
  times_vector_xmin <- as.POSIXct(times_vector_xmin)
  times_vector_xmax <- as.POSIXct(times_vector_xmax)

  # Initialiser le vecteur de résultats
  result_min <- vector("numeric", length(times_vector_xmin))
  result_max <- vector("numeric", length(times_vector_xmax))

  # Pour chaque temps, trouver la ligne correspondante
  for (i in seq_along(times_vector_xmin)) {
    time_min <- times_vector_xmin[i]
    matched_row_min <- data %>%
      filter(interval_start <= time_min & interval_end >= time_min)

    # Si une ligne correspond, extraire compressed_time
    if (nrow(matched_row_min) > 0) {
      result_min[i] <- matched_row_min$compressed_time[1]
    } else {
      result_min[i] <- NA  # Aucun match trouvé
    }
  }

  # Pour chaque temps, trouver la ligne correspondante
  for (i in seq_along(times_vector_xmax)) {
    time_max <- times_vector_xmax[i]
    matched_row_max <- data %>%
      filter(interval_start <= time_max & interval_end >= time_max)

    # Si une ligne correspond, extraire compressed_time
    if (nrow(matched_row_max) > 0) {
      result_max[i] <- matched_row_max$compressed_time[1]
    } else {
      result_max[i] <- NA  # Aucun match trouvé
    }
  }  
  
  df_areas <- data.frame(xmin = result_min, xmax = result_max, fill = fill)
  
  return(df_areas)
}

```

```{r}
plot_activity_with_areas <- function(data, nb_min, areas,
                                     title, subtitle,
                                     x_lab, y_lab) {

  # Créer le plot
  ggplot(data, aes(x = compressed_time, y = activity_proportion)) +
    geom_rect(data = areas,
              aes(xmin = xmin, xmax = xmax, ymin = -Inf, ymax = Inf, fill = fill),
              inherit.aes = FALSE, alpha = 0.2) +
    geom_line() +
    ylab(y_lab) +
    scale_x_continuous(name = x_lab,
                       breaks = seq(from = 0, to = nrow(data), by = 10)) +
    ggtitle(title,
            subtitle = paste(subtitle, "every", nb_min, "minutes."))
}

```

On a un gros trou au milieu au niveau de la quantité d'activité : c'est
cohérent, parce que le renard était sous anesthésie.

```{r}
from_data_to_plot <- function(data_8h_21h,
                              interval_seconds,
                              time_column = interval_start,
                              title,
                              subtitle,
                              x_lab,
                              y_lab){
  
  data_8h_21h_increasing_code <- posture_123(data_8h_21h)

  amount_activity_data <- amount_activity(data = data_8h_21h_increasing_code,
                                     interval_seconds = interval_seconds) # default = 900 seconds (15 minutes)

# remove the 21h-8h gap
  amount_activity_8h_21h <- filter_8h_21h(
    data = amount_activity_data,
    time_column = interval_start)


  # Compressed time variable to skip parts between 21h and 8h
  amount_activity_x_minutes_8h_21h_compressed_time <- add_compressed_time_variable(amount_activity_8h_21h)

  areas <- get_areas_color(data = amount_activity_x_minutes_8h_21h_compressed_time,
                            times_vector_xmin =
                              c("2022-07-04 08:00:00", #No data
                                "2022-07-04 18:57:00",
                                "2022-07-05 18:57:00",
                                "2022-07-04 10:47:00", #Inactive
                                "2022-07-04 13:17:00",
                                "2022-07-05 08:13:00",
                                "2022-07-06 08:50:00",
                                "2022-07-04 17:07:00", #Active
                                "2022-07-05 09:13:00",
                                "2022-07-06 09:50:00",
                                "2022-07-04 11:56:00"),#Out for implant
                            times_vector_xmax = 
                              c("2022-07-04 10:47:00", #No data
                                "2022-07-05 08:13:00",
                                "2022-07-06 08:50:00",
                                "2022-07-04 11:56:00", #Inactive
                                "2022-07-04 15:08:00",
                                "2022-07-05 09:13:00",
                                "2022-07-06 09:50:00",
                                "2022-07-04 18:57:00", #Active
                                "2022-07-05 10:22:00",
                                "2022-07-06 12:31:00",
                                "2022-07-04 13:17:00"),#Out for implant
                            fill =
                              c("No data", "No data", "No data",
                                "Inactive", "Inactive", "Inactive", "Inactive",
                                "Active", "Active", "Active",
                                "Out for implant"))
  
  plot <- plot_activity_with_areas(
    amount_activity_x_minutes_8h_21h_compressed_time,
    nb_min = interval_seconds/60,
    areas = areas,
    title = title,
    subtitle = subtitle,
    x_lab = x_lab,
    y_lab = y_lab)
  
  return(plot)

  }
```

```{r}
from_data_to_plot(data_8h_21h = data_8h_21h_04_to_12_07_2022,
                  interval_seconds = 3600,
                  title = "Posture's score of fox 4313",
                  subtitle = "With all data, from 04/07/2022 to 12/07/2022",
                  x_lab = "Cumulative time of the day (only between 8h and 21h)",
                  y_lab = "Movement score by summing posture indices")
```
