---
title: "SCP with QCC"
author: "Mathilda Alhamadah"
date: "2025-03-07"
output:
  html_document:
    toc: true             #table des matières
    toc_float: true       #table des matières toujours visible
    number_sections: true #numéroter sections
    theme: bootstrap      #changer le thème de la page
    highlight: zenburn    #changer le thème des chunks
---

# Firsts steps with QCC

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#install.packages("qcc")
library(qcc)
library(ggplot2)
library(slider)
```

## R chart vs xbar chart {.tabset}

Je crois bien que ces 2 charts font partie des Standard Shewhart control charts, qui peuvent être appelés directement avec la fonction qcc().\
On a une UCL (upper cotrol limit) et une LCL (lower control limit) avec la ligne horizontale qui représente le centre. Les limites sup et inf sont égales à ce centre +/- nsigma.

## Make groups

We have data with 5 observations per sample, 40 samples (sample), and a measure for each observation (diameter). We also have the information if the dataset is the train or the test phase (trial).

```{r, echo=FALSE, results=FALSE}
# Loading the piston rings data
data(pistonrings)
head(pistonrings)

# Make groups : lines = the sample number & columns = the repeated observations
diameter <- qcc.groups(data = pistonrings$diameter,
                       sample = pistonrings$sample)
head(diameter)
summary(diameter)
```

I think for us : lines = days & columns = mean of the indicator (already aggregated every x minutes) in that day. For example :

\| day 1 \| mean indicator1 8h \| mean indicator1 9h \| mean indicator1 10h \| ...

\| day 2 \| mean indicator1 8h \| mean indicator1 9h \| mean indicator1 10h \| ...

...

So that each mean already has its own sd

```{r}
qcc(data = diameter[1:25,],      #train dataset
    type = "xbar",               #chart type
    newdata = diameter[26:40,])  #test dataset
```

### Graphique R chart

```{r , results=FALSE}
obj <- qcc(diameter[1:30,], type="R")

summary(obj)
```

### Graphique xbar Chart

```{r, results=FALSE}
obj <- qcc(diameter[1:30,], type="xbar")

summary(obj)
```

## Changement du nsigma {.tabset}

**Nisgma** c'est pour définir les seuils sup et inf à partir desquels la valeur est problématique. Par défaut, **nsigma = 3**.

### Graphique nsigma à 2

```{r}
obj <- qcc(diameter[1:30,], type="xbar",nsigmas = 2)
```

### Graphique nsigma à 1

```{r}
obj <- qcc(diameter[1:30,], type="xbar",nsigmas = 1)
```

## Avec un autre jdd

```{r}
load("data_SCP_with_QCC.RData")   #data from Shewhart_indicator_3.Rmd
```

```{r}
# Créer un objet QCC
q <- qcc(data = posture_changes_byday_15min[1:10,],     
    type = "xbar",                                
    newdata = posture_changes_byday_15min[11:15,])

q$statistics #valeurs des points pour la période de calibration
q$newstats   #valeurs des points pour la période de test
q$limits     #valeurs UCL et LCL

# Avoir la taille des échantillons chaque jour
q$sizes     #période de calibration
q$newsizes  #période de test

# Avoir la valeur des points et la moyenne
stats.xbar(data = posture_changes_byday_15min[1:10,]) # center = 20.26108

# Avoir l'écart-type
sd.xbar(data = posture_changes_byday_15min[1:10,], 
        std.dev = "RMSDF") #default

#UWAVE-SD : 23.61101
#MVLUE-SD : 23.96539
#RMSDF : 24.34841

# Avoir les valeurs UCL et LCL (2ème méthode)
limits.xbar(center = stats.xbar(data = posture_changes_byday_15min[1:10,])$center,
            std.dev = sd.xbar(data = posture_changes_byday_15min[1:10,], std.dev = "RMSDF"),
            sizes = q$sizes,
            conf = q$nsigmas) 

# Avoir les points oranges et rouges
q$violations

#$beyond.limits = points rouges
#$violating.runs = points oranges

# Pareil
shewhart.rules(q,
               limits = q$limits,
               run.length = qcc.options("run.length")) #default = 7, max value of a run before to signal an OOC point


# Avoir les points rouges
beyond.limits(q,
              limits = q$limits)

# Avoir les points oranges 
violating.runs(q,
               run.length = 7) #7 = default

# Connaître toutes les options par défaut de QCC
qcc.options()

# Changer les options par défaut QCC
default <- qcc.options()             #sauvegarder les options par défaut
qcc.options(run.length = 4)

qcc(data = posture_changes_byday_15min[1:10,],     
    type = "xbar",                                
    newdata = posture_changes_byday_15min[11:15,],
    nsigmas = 3)

qcc.options(default)                  #rétablir les options par défaut

```

## Personnalisation des seuils & règles d'out of control (OOC)

On a peu d'options de personnalisation pour les règles d'OOC :

-   On peut choisir `exp.R.unscaled` pour donner les valeurs attendues du rapport R/sigma pour une distribution normale. Utile pour calculer les facteurs tq d2 dans les tableaux de contrôle de qualité ⇒ agit sur le calcul des limites

-   On peut choisir `se.R.unscaled` pour donner les erreurs standards du rapport R/sigma. Utile pour estimer la variabilité de la plage de données, correspond au facteur d3 dans les tableaux de contrôle de qualité ⇒ agit sur le calcul des limites

-   On peut choisir `run.length` pour donner le nombre maximum de points se trouvant du même côté de la moyenne avant qu’on considère que c’est inquiétant

=\> Pour le reste, si on veut rajouter des règles pour mettre les points en orange par ex (ou en jaune pour des règles 2ndaires), il faut les créer nous-mêmes.

**Articles utiles :**

Pas mal d'infos sur QCC : <https://cran.r-project.org/web/packages/qcc/qcc.pdf>

Règles souvent utilisées pour Shewhart : <https://analyse-it.com/docs/user-guide/process-control/shewhart-control-chart-rules> et <https://luca-scr.github.io/qcc/reference/rules.html>

Comprendre l'argument run.length : <https://stackoverflow.com/questions/61882255/how-does-it-works-the-argument-run-length-of-the-fuction-qcc-options>

Attention pour un xbar chart par défaut l'écart-type est calculé avec la méthode "UWAVE-R" mais si y'a ne serait-ce qu'une donnée NA pour toute une plage de temps on passe automatiquement sur la méthode RMSDF : <https://documentation.sas.com/doc/fr/pgmsascdc/v_065/qcug/qcug_shewhart_sect353.htm>

## Personnalisation graphique & ggplot2

On a aussi quelques options de **personnalisation graphique**, faire `?qcc.options` pour les voir. Possible aussi d'aller voir sur ce site mais pour moi ça a pas marché (obsolète ?) : <https://luca-scr.github.io/qcc/reference/qccGroups.html>

Sinon, faire en sorte que les plots s'affichent directement en ggplot2 pour pouvoir les modifier, télécharger le fichier qcc.plot.R ici : <https://github.com/tomhopper/qcc_ggplot>

-\> Mettre ce fichier dans le dossier de codes R où on travaille, et faire `source("qcc.plot.R")`. Maintenant quand on fait un graphe qcc il est en ggplot2 et on peut le modifier ! Les plots qcc sont remis par défaut à chaque redémarrage de R.

Pour faire plusieurs plots en un, utiliser le package ggpubR : <https://www.rdocumentation.org/packages/ggpubr/versions/0.6.1>

```{r}
source(file = "qcc.plot.R") #changer le style des graphiques QCC par défaut
```

```{r}
myplot <- qcc(data = posture_changes_byday_15min[1:10,],     
    type = "xbar",                                
    newdata = posture_changes_byday_15min[11:15,],
    nsigmas = 3, 
    digits = 4,  #only 4 "digits" (for example 17,62 is considered 4 digits wtf)
    title = "Xbar chart for indicator 3 : posture changes by day",  #title
    font.size = 14,  #size of the title + the axes
    cex = 3,         #size of the dots
    new.plot = TRUE) #useless for me, creates a new graph (for multi-pannels charts)

```

Mais on peut pas modifier plus que ça. Plutôt essayer de le construire directement dans ggplot2 :

```{r}
# Data preparation for ggplot2

  # Create QCC object
q <- qcc(data = posture_changes_byday_15min[1:10,],     
    type = "xbar",                                
    newdata = posture_changes_byday_15min[11:15,])

  # Dataframe with needed information
qcc_data <- data.frame(
  Date = seq(1,(length(q$statistics) + length(q$newstats)), 1),
  Value = rep(NA,15),
  UCL = q$limits[, 2],
  LCL = q$limits[, 1],
  Nb_values = rep(NA,15))

  # Adapt dataframe
qcc_data$Value[1:10] <- q$statistics     #fill Value variable
qcc_data$Value[11:15] = q$newstats

qcc_data$Date[1:10] <- rownames(q$data)  #fill Date variable
qcc_data$Date[11:15] <- rownames(q$newdata)

qcc_data$Date <- factor(qcc_data$Date, levels = qcc_data$Date) #Date as factor

qcc_data$Nb_values[1:10] <- q$sizes      #fill Nb_values variable
qcc_data$Nb_values[11:15] <- q$newsizes

  # Add variable of 1 SD (the value depends on the amount of NA during this day)
qcc_data$SD <- q$std.dev/sqrt(qcc_data$Nb_values) #get 2sd & 3sd by multiplying

  # Make a TRUE/FALSE variable if OOC or not
qcc_data$Out_3sd <- with(qcc_data, Value > UCL | Value < LCL)
qcc_data$Out_2sd <- with(qcc_data, Value > q$center+2*SD | Value < q$center-2*SD)
qcc_data$Out_1sd <- with(qcc_data, Value > q$center+SD | Value < q$center-SD)

  # Add conditions for rule3 (4/5 following points > 1sigma from the center)

      # Check if each point is at <1sd distance from mean + check if up/down
qcc_data <- qcc_data %>%
  mutate(more_1sd_distance = case_when(
    Value > q$center + SD ~ 1,  #more than 1sd distance from mean, positive side
    Value < q$center - SD ~ -1, #more than 1sd distance from mean, negative side
    TRUE ~ 0                  #within [mean +/- 1sd]
  )) %>%
      # Check if 4/5 following points are >1sd distance from mean on the same side
  mutate(Rule3 = slide_int(more_1sd_distance, ~{
    pos <- sum(.x == 1)       #sum the >1 sd positive side
    neg <- sum(.x == -1)      #sum the >1 sd negative side
    if(pos >= 4 | neg >= 4) TRUE else FALSE  #T if 4 points >1 sd on the same side
  }, .before = 4,             #we watch the 4 previous points (+ the current point)
  .complete = TRUE))          #do nothing (= NA) if there are not 4 previous points


  # Add conditions for rule4 (6 following points are increasing/ decreasing : trend)

    # Check if each point is an increase or a decrease compared to the previous one
qcc_data <- qcc_data %>% 
  mutate(increase_decrease = case_when(
    Value > lag(Value) ~ 1,  #it's an increase
    Value < lag(Value) ~ -1, #it's a decrease
    Value == lag(Value) ~ 0, #it's the same value
    TRUE ~ 0                 #there is no previous
  )) %>% 
  mutate(Rule4 = slide_int(increase_decrease, ~{
    inc <- sum(.x == 1)      #sum the increases
    dec <- sum(.x == -1)     #sum the decreases
    if( inc >= 6 | dec >= 6) TRUE else FALSE  #T if more than 6 neighbours inc/dec
  }, .before = 5,            #watch 5 previous points (+ the current point)
  .complete = TRUE ))        #do nothing (= NA) if there are not 5 previous points


  #Add conditions for Rule5 (7 following points up/down the mean)

    # Check for each point if it's up/ down the mean
qcc_data <- qcc_data %>%
  mutate(up_down_mean = case_when(
    Value > q$center ~ 1,  #up to the mean
    Value < q$center ~ -1, #down the mean
    TRUE ~ 0             #it's the mean
  )) %>%
      # Check if 7 following points are on the same side from the mean
  mutate(Rule5 = slide_int(up_down_mean, ~{
    up <- sum(.x == 1)       #sum the upside points
    down <- sum(.x == -1)    #sum the downside points
    if(up >= 7 | down >= 7) TRUE else FALSE  #T if 7 points on the same side
  }, .before = 6,             #we watch the 6 previous points (+ the current point)
  .complete = TRUE))          #do nothing (= NA) if there are not 6 previous points


  # Add the 4 rules to a variable indicating if a rule is violated and which one

qcc_data <- qcc_data %>% 
  mutate(OutOfControl = case_when(
    
    # The 4 rules I want on my chart
    # from less to most important so that most important rule is the last remembered
    Rule5 > 0 ~ "Rule 5",
    Rule4 > 0 ~ "Rule 4",
    Rule3 > 0 ~ "Rule 3",
    Out_2sd == TRUE & (lag(Out_2sd) == T | lag(lag(Out_2sd == T))) ~ "Rule 2",
    Out_3sd == TRUE ~ "Rule 1",
    TRUE ~ "In control"))
```

```{r}
# Plot the graph

ggplot(qcc_data, aes(x = Date)) +
    # Lines
  geom_hline(aes(yintercept = Center[1]), color = "red", linetype = "solid") + #Mean
  geom_line(aes(y = Value, group = 1), color = "black") +
  geom_line(aes(y = UCL, group = 1), color = "blue", linetype = "solid") + #UCL
  geom_line(aes(y = LCL, group = 1), color = "blue", linetype = "solid") + #LCL
      #2SD
  geom_line(aes(y = Center[1] + 2*SD,
                group = 1), color = "blue", linetype = "dashed" ) +  #+2 sd
  geom_line(aes(y = Center[1] - 2*SD,
                group = 1), color = "blue", linetype = "dashed" ) +  #-2 sd
    # Dots
  geom_point(aes(y = Value, color = OutOfControl), size = 2) +
    # Legend
  scale_color_manual(values = c(
    "Rule 1" = "red",
    "Rule 2" = "orange",
    "Rule 3" = "orange",
    "Rule 4" = "gold",
    "Rule 5" = "gold",
    "In control" = "black"
  )) +
    # Labels
  labs(
    title = "Xbar chart for indicator 3 : posture changes by day",
    subtitle = "Every 15min, for fox 4313",
    x = "Date",
    y = "Amount of posture changes",
    color = "Out of control data"
  ) +
  theme_minimal() +
    # Rotate axis labels (dates)
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

## Automatisation

```{r}
# Automatized data preparation for ggplot2

data_prep_xbarchart_ggplot <- function(data_calibration,
                                 data_test){
  
    # Create variables
  n_calib <- nrow(data_calibration)
  n_total <- nrow(data_calibration) + nrow(data_test)
  
    # Create QCC object
  q <- qcc(data = data_calibration,     
      type = "xbar",                                
      newdata = data_test, plot = FALSE)
  
    # Dataframe with needed information
  qcc_data <- data.frame(
    Date = seq(1,(length(q$statistics) + length(q$newstats)), 1),
    Value = rep(NA, n_total), #vector of NA, same length as total observations
    UCL = q$limits[, 2],      #get UCL from QCC
    LCL = q$limits[, 1],      #get LCL from QCC
    Nb_values = rep(NA, n_total))  #vector of NA, same length as total observations
  
    # Adapt dataframe
  qcc_data$Value[1:n_calib] <- q$statistics     #fill Value variable
  qcc_data$Value[(n_calib+1):n_total] = q$newstats
  qcc_data$Date[1:n_calib] <- rownames(q$data)  #fill Date variable
  qcc_data$Date[(n_calib+1):n_total] <- rownames(q$newdata)

  qcc_data$Date <- factor(qcc_data$Date, levels = qcc_data$Date) #Date as factor

  qcc_data$Nb_values[1:n_calib] <- q$sizes      #fill Nb_values variable
  qcc_data$Nb_values[(n_calib+1):n_total] <- q$newsizes

    # Add variable of 1 SD (the value depends on the amount of NA during this day)
  qcc_data$SD <- q$std.dev/sqrt(qcc_data$Nb_values) #get 2sd & 3sd by multiplying

    # Make a TRUE/FALSE variable if OOC or not
  qcc_data$Out_3sd <- with(qcc_data, Value > UCL | Value < LCL)
  qcc_data$Out_2sd <- with(qcc_data, Value > q$center+2*SD | Value < q$center-2*SD)
  qcc_data$Out_1sd <- with(qcc_data, Value > q$center+SD | Value < q$center-SD)

  
    # Add conditions for rule3 (4/5 following points > 1sigma from the center)
  
        # Check if each point is at <1sd distance from mean + check if up/down
  qcc_data <- qcc_data %>%
    mutate(more_1sd_distance = case_when(
      Value > q$center + SD ~ 1,  #more than 1sd distance from mean, positive side
      Value < q$center - SD ~ -1, #more than 1sd distance from mean, negative side
      TRUE ~ 0                  #within [mean +/- 1sd]
    )) %>%
        # Check if 4/5 following points are >1sd distance from mean on the same side
    mutate(Rule3 = slide_int(more_1sd_distance, ~{
      pos <- sum(.x == 1)       #sum the >1 sd positive side
      neg <- sum(.x == -1)      #sum the >1 sd negative side
      if(pos >= 4 | neg >= 4) TRUE else FALSE  #T if 4 points >1 sd on the same side
    }, .before = 4,             #we watch the 4 previous points (+ the current point)
    .complete = TRUE))          #do nothing (= NA) if there are not 4 previous points
  
  
    # Add conditions for rule4 (6 following points are increasing/ decreasing : trend)
  
      # Check if each point is an increase or a decrease compared to the previous one
  qcc_data <- qcc_data %>% 
    mutate(increase_decrease = case_when(
      Value > lag(Value) ~ 1,  #it's an increase
      Value < lag(Value) ~ -1, #it's a decrease
      Value == lag(Value) ~ 0, #it's the same value
      TRUE ~ 0                 #there is no previous
    )) %>% 
    mutate(Rule4 = slide_int(increase_decrease, ~{
      inc <- sum(.x == 1)      #sum the increases
      dec <- sum(.x == -1)     #sum the decreases
      if( inc >= 6 | dec >= 6) TRUE else FALSE  #T if more than 6 neighbours inc/dec
    }, .before = 5,            #watch 5 previous points (+ the current point)
    .complete = TRUE ))        #do nothing (= NA) if there are not 5 previous points


    #Add conditions for Rule5 (7 following points up/down the mean)
  
      # Check for each point if it's up/ down the mean
  qcc_data <- qcc_data %>%
    mutate(up_down_mean = case_when(
      Value > q$center ~ 1,  #up to the mean
      Value < q$center ~ -1, #down the mean
      TRUE ~ 0             #it's the mean
    )) %>%
        # Check if 7 following points are on the same side from the mean
    mutate(Rule5 = slide_int(up_down_mean, ~{
      up <- sum(.x == 1)       #sum the upside points
      down <- sum(.x == -1)    #sum the downside points
      if(up >= 7 | down >= 7) TRUE else FALSE  #T if 7 points on the same side
    }, .before = 6,             #we watch the 6 previous points (+ the current point)
    .complete = TRUE))          #do nothing (= NA) if there are not 6 previous points


    # Add the 4 rules to a variable indicating if a rule is violated and which one
  
  qcc_data <- qcc_data %>% 
    mutate(OutOfControl = case_when(
      
      # The 4 rules I want on my chart
      # from less to most important so that most important rule is the last remembered
      Rule5 > 0 ~ "Rule 5",
      Rule4 > 0 ~ "Rule 4",
      Rule3 > 0 ~ "Rule 3",
      Out_2sd == TRUE & (lag(Out_2sd) == T | lag(lag(Out_2sd == T))) ~ "Rule 2",
      Out_3sd == TRUE ~ "Rule 1",
      TRUE ~ "In control"))
  
  output <- list(qcc_data, q$center)
  
    # Return data
  return(output)
  
}

#Test
# data_and_center <- data_prep_xbarchart_ggplot(data_calibration = posture_changes_byday_15min[1:10,],
#                            data_test = posture_changes_byday_15min[11:15,])




```

```{r}
plot_xbarchart_ggplot <- function(data_calibration,
                                  data_test,
                                  title,
                                  subtitle,
                                  indicator_name
                                  ){
  
  # Get the data & the center
  data_and_center <- data_prep_xbarchart_ggplot(data_calibration = data_calibration,
                                                data_test = data_test) #prepare data
  qcc_data <- data_and_center[[1]] #get the data
  center <- data_and_center[[2]]   #get the mean value for calibration period
  
  # Plot the graph
  
  ggplot(qcc_data, aes(x = Date)) +
      # Lines
    geom_hline(aes(yintercept = center), color = "red", linetype = "solid") + #Mean
    geom_line(aes(y = Value, group = 1), color = "black") +
    geom_line(aes(y = UCL, group = 1), color = "blue", linetype = "solid") + #UCL
    geom_line(aes(y = LCL, group = 1), color = "blue", linetype = "solid") + #LCL
        #2SD
    geom_line(aes(y = center + 2*SD,
                  group = 1), color = "blue", linetype = "dashed" ) +  #+2 sd
    geom_line(aes(y = center - 2*SD,
                  group = 1), color = "blue", linetype = "dashed" ) +  #-2 sd
      # Dots
    geom_point(aes(y = Value, color = OutOfControl), size = 2) +
      # Legend
    scale_color_manual(values = c(
      "Rule 1" = "red",
      "Rule 2" = "orange",
      "Rule 3" = "orange",
      "Rule 4" = "gold",
      "Rule 5" = "gold",
      "In control" = "black"
    )) +
      # Labels
    labs(
      title = title,
      subtitle = subtitle,
      x = "Date",
      y = indicator_name,
      color = "Out of control data"
    ) +
    theme_minimal() +
      # Rotate axis labels (dates)
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
}
```

And finally, let's plot the graph !

```{r}
# Test for 15min timestep
plot_xbarchart_ggplot(data_calibration = posture_changes_byday_15min[1:10,],
                      data_test = posture_changes_byday_15min[11:15,],
                      title = "Xbar chart for indicator 3 : posture changes by day",
                      subtitle = "Every 15min, for fox 4313",
                      indicator_name = "Amount of posture changes")

# Test for 4h timestep
plot_xbarchart_ggplot(data_calibration = posture_changes_byday_4h[1:10,],
                      data_test = posture_changes_byday_4h[11:15,],
                      title = "Xbar chart for indicator 3 : posture changes by day",
                      subtitle = "Every 4h, for fox 4313",
                      indicator_name = "Amount of posture changes")
```
