---
title: "Shewhart indicator 3"
author: "Mathilda Alhamadah"
date: "2025-07-21"
output: html_document
---

# 0. Starter

```{r}
library(qcc)
library(jsonlite)
library(purrr)
library(curl)
library(dplyr)
library(lubridate)
library(tidyr)
library(ggplot2)
library(patchwork)
```

# 1. Load data

```{r}
load("data_QCC_indicator3_complete_reliable_15min_to_6h.RData")
```


## → How to get this data ?

```{r}
load("reliable_data_8h_21h_05_07_to_08_08_2022.RData")
```

```{r}
# Function 1 : Detect time changes

amount_posture_changes <- function(
    data,
    time_seconds){ 
  
  # Temporary variable : not_visible & NAs replaced by NAs
  data <- data %>% 
    mutate(posture_no_NA = case_when(
      name == "not visible" ~ NA,  #NA if not visible
      is.na(name) ~ NA,            #NA if NA
      TRUE ~ name)                 #else : posture name
      )  
  
  # Refill NAs (= real NAs + not_visible) with latest posture seen
  data <- data %>%
    fill(posture_no_NA)           
  
  
  # Detect position changes
  data_valid <- data %>%
    arrange(Date_Time) %>%  #Sort by date
    # Movement : if posture != posture at previous time (skip NAs & not_visible)
    mutate(Position_change = posture_no_NA != lag(posture_no_NA, default = first(posture_no_NA)))

  # Final dataset
  result <- changes_by_group_time(data_valid, time_gap = time_seconds)
  
  # Remove data if too many NAs
    
    
      # Set the allowed % of NAs depending on time intervals
    if(time_seconds < 3600){      #if groups < 1h
      proportion_NA <- 0.05               #max 5% of NA
    }else{
      proportion_NA <- 0.5                #else : max 50% of NA
    }
    
      # Maximum amount of NAs by interval, depending on interval length
    max_na <- floor(time_seconds*proportion_NA) #round if not integer
    
      # If too much NAs in interval : interval is NA
    result <- result %>% 
      mutate(Nb_changes = ifelse(Nb_NA > max_na, NA, Nb_changes)) 
    
      # If the time_group starts at 21h, set value to NA because there is only 1 data (maximum)
      # Other way to do : provide creating a time group starting at 21h because maximum 1 data
    result[hour(result$Time_group)==21,]$Nb_changes <- NA
    
      # Return result
      return(result)
  
  }



# Function 2 : Get the sum of posture changes by time unit

changes_by_group_time <- function(data, time_gap) {
  data %>%
    arrange(Date_Time) %>% #order by date & time
    
    #make time groups
    mutate(Time_group =
             as.POSIXct(floor                   # floor = to give the same value to all the dates that should be in the same time group
                        (as.numeric(Date_Time)  #convert every date into a number
                          / time_gap)           #so that doing +1 = changing of interval
                                   * time_gap,  #group dates by time_gap intervals
      origin = "1970-01-01")) %>% #convert numbers back to dates (origin = the reference date used by POSIXct. It was also used as a reference when we did as.numeric(Date_Time), but it was implicit)
    
    group_by(Time_group) %>%      #create groups
    summarise(                    #to make only 1 line per group & sum up the informations of all the lines
      Nb_changes = sum(Position_change, na.rm = TRUE), #number of changes = sum of changes
      Nb_NA = sum(is.na(name))                         #sum NAs
    ) %>%
    ungroup()               #always ungroup after group_by
}

```

```{r}
# Number of changes :

  # per 15minutes
amount_changes_15min_data_8h_21h_05_07_to_08_08_2022 <- amount_posture_changes(reliable_data_8h_21h_05_07_to_08_08_2022, 900)

  # per 30minutes
amount_changes_30min_data_8h_21h_05_07_to_08_08_2022 <- amount_posture_changes(reliable_data_8h_21h_05_07_to_08_08_2022, 1800)

  # per 1h
amount_changes_1h_data_8h_21h_05_07_to_08_08_2022 <- amount_posture_changes(reliable_data_8h_21h_05_07_to_08_08_2022, 3600)

  # per 2h
amount_changes_2h_data_8h_21h_05_07_to_08_08_2022 <- amount_posture_changes(reliable_data_8h_21h_05_07_to_08_08_2022, 7200)

  # per 4h
amount_changes_4h_data_8h_21h_05_07_to_08_08_2022 <- amount_posture_changes(reliable_data_8h_21h_05_07_to_08_08_2022, 14400)

  # per 6h
amount_changes_6h_data_8h_21h_05_07_to_08_08_2022 <- amount_posture_changes(reliable_data_8h_21h_05_07_to_08_08_2022, 21600)
```

Create a day variable to aggregate by day
```{r}
# per 15min
amount_changes_15min_data_8h_21h_05_07_to_08_08_2022 <- amount_changes_15min_data_8h_21h_05_07_to_08_08_2022 %>%
  mutate(day = as.Date(Time_group))

# per 30min
amount_changes_30min_data_8h_21h_05_07_to_08_08_2022 <- amount_changes_30min_data_8h_21h_05_07_to_08_08_2022 %>%
  mutate(day = as.Date(Time_group))

# per 1h
amount_changes_1h_data_8h_21h_05_07_to_08_08_2022 <- amount_changes_1h_data_8h_21h_05_07_to_08_08_2022 %>%
  mutate(day = as.Date(Time_group))

# per 2h
amount_changes_2h_data_8h_21h_05_07_to_08_08_2022 <- amount_changes_2h_data_8h_21h_05_07_to_08_08_2022 %>%
  mutate(day = as.Date(Time_group))

# per 4h
amount_changes_4h_data_8h_21h_05_07_to_08_08_2022 <- amount_changes_4h_data_8h_21h_05_07_to_08_08_2022 %>%
  mutate(day = as.Date(Time_group))

# per 6h
amount_changes_6h_data_8h_21h_05_07_to_08_08_2022 <- amount_changes_6h_data_8h_21h_05_07_to_08_08_2022 %>%
  mutate(day = as.Date(Time_group))
```

Here we are ! You can still download the data here :
```{r}
load("data_QCC_indicator3_complete_reliable_15min_to_6h.RData")
```


# 2. Aggregate by day

```{r}
# 15min
posture_changes_byday_15min <- qcc.groups(
  data = amount_changes_15min_data_8h_21h_05_07_to_08_08_2022$Nb_changes,
  sample = amount_changes_15min_data_8h_21h_05_07_to_08_08_2022$day)

# 30min
posture_changes_byday_30min <- qcc.groups(
  data = amount_changes_30min_data_8h_21h_05_07_to_08_08_2022$Nb_changes,
  sample = amount_changes_30min_data_8h_21h_05_07_to_08_08_2022$day)

# 1h
posture_changes_byday_1h <- qcc.groups(
  data = amount_changes_1h_data_8h_21h_05_07_to_08_08_2022$Nb_changes,
  sample = amount_changes_1h_data_8h_21h_05_07_to_08_08_2022$day)

# 2h
posture_changes_byday_2h <- qcc.groups(
  data = amount_changes_2h_data_8h_21h_05_07_to_08_08_2022$Nb_changes,
  sample = amount_changes_2h_data_8h_21h_05_07_to_08_08_2022$day)

# 4h
posture_changes_byday_4h <- qcc.groups(
  data = amount_changes_4h_data_8h_21h_05_07_to_08_08_2022$Nb_changes,
  sample = amount_changes_4h_data_8h_21h_05_07_to_08_08_2022$day)

# 6h
posture_changes_byday_6h <- qcc.groups(
  data = amount_changes_6h_data_8h_21h_05_07_to_08_08_2022$Nb_changes,
  sample = amount_changes_6h_data_8h_21h_05_07_to_08_08_2022$day)
```


# 3. Xbar chart

Here we don't have the NA data between 14/07 & 05/08 : the table only contains dates that have data. So calibration phase = from 05/07 to 14/07 (lines 1 to 10 in the table) & test phase = from 03/08 to 08/08, without 04/08 (missing) =lines 11 to 15 in the table. There is 1 more column than it should be (53 instead of 52 for 15min aggregation for example), but it's only because of the 21h interval : it shouldn't change anything.

```{r}
# Charts

  #timesteps = 15min, 1point = 1day
qcc(data = posture_changes_byday_15min[1:10,],     #first 10 days = calibration
    type = "xbar",                                #chart type
    newdata = posture_changes_byday_15min[11:15,]) #last 4 days = test

  #timesteps = 30min, 1point = 1day
qcc(data = posture_changes_byday_30min[1:10,],     #first 10 days = calibration
    type = "xbar",                                #chart type
    newdata = posture_changes_byday_30min[11:15,]) #last 4 days = test

  #timesteps = 1h, 1point = 1day
qcc(data = posture_changes_byday_1h[1:10,],     #first 10 days = calibration
    type = "xbar",                                #chart type
    newdata = posture_changes_byday_1h[11:15,]) #last 4 days = test

  #timesteps = 2h, 1point = 1day
qcc(data = posture_changes_byday_2h[1:10,],     #first 10 days = calibration
    type = "xbar",                                #chart type
    newdata = posture_changes_byday_2h[11:15,]) #last 4 days = test

  #timesteps = 4h, 1point = 1day
qcc(data = posture_changes_byday_4h[1:10,],     #first 10 days = calibration
    type = "xbar",                                #chart type
    newdata = posture_changes_byday_4h[11:15,]) #last 4 days = test

  #timesteps = 6h, 1point = 1day
qcc(data = posture_changes_byday_6h[1:10,],     #first 10 days = calibration
    type = "xbar",                                #chart type
    newdata = posture_changes_byday_6h[11:15,]) #last 4 days = test
```
=> We do have an alert during the symptomatic phase, good thing. But afterwards the indicator is very normal. However, we do have an alert just before the death, so even if it's not soon enough to do someting to prevent it, it's good to see that we can see the problem when it occurs.






