---
title: "Shewhart indicator 1.3"
author: "Mathilda Alhamadah"
date: "2025-07-21"
output: html_document
---

# 0. Starter

# 1. Load data

Load the data here :

```{r}

```


## → But how to get this data ?

1st load or create the data from 05 to 14 of July with only reliable data & without anesthesia data :

```{r}
# Load the 05-14 of July data
load("reliable_data_8h_21h_05_to_14_07_2022.Rdata")
```

Then load the frequency_position function from file indicator_1 :

```{r}
# Frequency of postures lying/ sitting/ standing by timestep (chosen)

frequency_position <- function(data,
                               interval_seconds,
                               existing_data_percent) {
  data <- data %>% arrange(Date_Time) #sort by date
  
  start_time <- min(data$Date_Time)   #oldest frame
  end_time <- max(data$Date_Time)     #newest frame
  
  #Cut between these 2 frames depending on the time interval
  intervals <- seq(from = start_time, to = end_time, by = interval_seconds)
  
  
  df_counts <- data.frame(                       #create the new df
    start_time = intervals[-length(intervals)],  #drop the last time
    end_time = intervals[-1]                     #drop the first time
  )
  
  #Create the 4 posture variables
  df_counts <- df_counts %>%
    rowwise() %>%               #for each line
    mutate(
      lying = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 0, na.rm = TRUE),       #count lying
      standing = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 1, na.rm = TRUE),       #count standing
      sitting = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 2, na.rm = TRUE),       #count sitting
      not_visible = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 3, na.rm = TRUE)      #count not visible
    )
  
  #But keep it as numbers only if at least x% of data are not NA
  df_counts <- df_counts %>%
    #for those 4 columns
    mutate(across(c(sitting, standing, lying, not_visible),
                  #if less than x% of existing data
                  ~ if_else(sum(sitting, lying, standing, not_visible, na.rm = TRUE)/interval_seconds < (existing_data_percent / 100),
                            #then assign NA to each variable
                            NA,
                            #else : do nothing
                            .)))

  return(df_counts)
}
```

Then apply it to the data :

```{r}
# Compute the frequency of each posture
frequency_position_05_to_14_07_2022_15min <-
  frequency_position(data = reliable_data_8h_21h_05_to_14_07_2022, #data
                     interval_seconds = 900, #15min
                     existing_data_percent = 95)  #max 5% of NA data
```

Then sum the sitting & standing occurences (vs lying & not visible) :

```{r}
# Sum the standing & sitting occurences
frequency_position_05_to_14_07_2022_StandingSitting_15min <- frequency_position_05_to_14_07_2022_15min %>% 
  mutate(sitting_standing = sum(sitting, standing),
         lying_not_visible = sum(lying, not_visible)) #maybe useless but maybe not
```

Then we want each line to be a posture (sitting & standing vs lying & not_visible)

```{r}
# Pivot the data
frequency_position_05_to_14_07_2022_StandingSitting_15min_PIVOT <- pivot_data(data = frequency_position_05_to_14_07_2022_StandingSitting_15min,
                   variables_to_drop = c(end_time, lying, sitting, standing, not_visible),
                   variables_to_merge = c(sitting_standing, lying_not_visible),
                   str_name_merged_labels = "Aggregated_postures",
                   str_name_merged_values = "Count")
```

Then we want to remove the 21h-8h part that we unvolontary recreated :

```{r}
# Keep only the 8h-21h part
frequency_position_8h_21h_05_to_14_07_2022_StandingSitting_15min_PIVOT <- filter_8h_21h(frequency_position_05_to_14_07_2022_StandingSitting_15min_PIVOT, start_time)
# Remove useless
rm(frequency_position_05_to_14_07_2022_StandingSitting_15min_PIVOT)  #remove data with the 21h-8h gap
```

Than we want a new variable to replace the time since we have time gaps to fill :

```{r}
# Add a compressed_time variable
frequency_position_8h_21h_05_to_14_07_2022_StandingSitting_15min_PIVOT_compressed_time <- add_compressed_time_variable_PIVOT_data(frequency_position_8h_21h_05_to_14_07_2022_StandingSitting_15min_PIVOT, nbrep = 2)
```

And finally we want to have the time spent sitting/ standing but as a proportion :

```{r}
# Add a proportion variable
frequency_position_8h_21h_05_to_14_07_2022_StandingSitting_15min_PIVOT_compressed_time<- add_proportion(frequency_position_8h_21h_05_to_14_07_2022_StandingSitting_15min_PIVOT_compressed_time,
                      count_variable = Count,
                      period_duration = 900)  #15 mintues by time period = 900 seconds
```

# 2. Prepare data

# 3. Xbar chart