---
title: "Shewhart with QCC"
author: "Mathilda Alhamadah"
date: "2025-07-04"
output: html_document
---
# Starter

## What do we do

We're going to run the Shewhart algorithm using the QCC package on our data from 04 to 14th of July, 2022.
Shewhart because it's the easiest to begin & QCC because it doesn't use a real time metric so it's useful for our incomplete data with a "false" time metric (aggregating days but skipping the 21h-8h part). Also QCC is practical because of NA management : accepted (unless it's a whole day).

## Hypothesis

Data = realizations of iid random variable (VA), follows a normal distribution, no trend or cyclicity in data.
Possible with non normal data (ref : Clement, 2017) but not very clear about that.

## Pros

Simple to implement & interpret. Allows a quick detection of sudden & important changes in the process.
No need to transform data : we directly plot the process. We only build upper control limit (UCL) & lower control limit (LCL)

## Cons

Not very sensitive to small changes.


```{r}
library(qcc)
library(jsonlite)
library(purrr)
library(curl)
library(dplyr)
library(lubridate)
library(tidyr)
library(ggplot2)
library(patchwork)
```
```{r}

```

# Load data

## But how to get this data ?

Start from the data directly obtained with YOLO (see doc Read_Json_files) :
* But without anesthesia data (= data of the 05/07 + data of the 08/07 only between 9h6m57 and 10h14m09s)
* And without non reliable data (= data with a confidence < 1/3 ~ 0.34, and if > 2 predictions data with a confidence_gap < 0.2 between the 2 most reliable predictions)
* And without data outside 8h-21h

```{r}
#You can load it here :
load("reliable_data_8h_21h_05_to_14_07_2022.Rdata")
```

Then go to file Indicator_1 and run the whole "Functions" part. Now for each timestep you want, run this (example with 15min) :

```{r}
#interval_seconds = the timestep you want in seconds. Here : 15min*60 = 900 seconds.
frequency_position_15min_05_to_14_07_2022 <- frequency_position(data = reliable_data_8h_21h_05_to_14_07_2022, #data
                                                                interval_seconds = 900)                       #15min
```

But this made us have lines outside the 8h-21h gap again. We want to remove them :

```{r}
#function
filter_8h_21h <- function(data, time_column){
  data <- data %>%
    filter(hour({{time_column}}) >= 8 & hour({{time_column}}) < 21)
  return(data)
}

#apply function
frequency_position_6h_8h_21h_05_to_14_07_2022 <- filter_8h_21h(data = frequency_position_6h_05_to_14_07_2022,
                                                            time_column = start_time)

rm(frequency_position_6h_05_to_14_07_2022) #remove useless data
```

Now we need to remove again data of day 08/07 between 9h6m57 and 10h14m09s. Since they have already been removed in the original "reliable_data...", their value is 0 for each variable. But we don't want to have zeros if we removed the data, we want to have NAs. So we are just going to assign "NA" to these data so that it won't mess up because of missing lines :

```{r}
frequency_position_6h_8h_21h_05_to_14_07_2022 <- frequency_position_6h_8h_21h_05_to_14_07_2022 %>%
  mutate(
      #Define what's in the time we want to drop
    in_interval = end_time >= as.POSIXct("2022-07-08 09:06:57") & start_time <= as.POSIXct("2022-07-08 10:14:09"),
      #If in the time : NA, else : normal value
    sitting = if_else(in_interval, NA, sitting),
    standing = if_else(in_interval, NA, standing),
    lying = if_else(in_interval, NA, lying),
    not_visible = if_else(in_interval, NA, not_visible)
  ) %>%
  select(-in_interval)  #Remove temporary variable

```

Warning : this is the most restrictive removal we can do. For example if the timestep is 2hours it will make the whole line go to NA. But if we want to be less restrictive, we just have to switch end_time and start_time : it will remove only lines that have both end_time and start_time in the interval. Whereas here, we remove lines if they have at least one time in the interval. I know it sounds weird but it works, the difference is about overlap of intervals : does it have to be partial or total to be NA ? Most restrictive (our case) = partial.

Now we want to create a day variable to aggregate by day :

```{r}
frequency_position_6h_8h_21h_05_to_14_07_2022 <- frequency_position_6h_8h_21h_05_to_14_07_2022 %>%
  mutate(day = as.Date(start_time))
```

Now we're all done ! Do that for every timestep you want to try. You can load the final data here :

```{r}
#15 min
load()
#30 min
load()
#1 hour
load()
#2 hours
load()
#4 hours
load()
#6 hours
load()
```


# QCC charts

```{r}
#Aggregate by day with QCC function

  # function

aggregate_by_day <- function(frequency_position_data, time) {
  
  variable_name <- paste("lying_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$lying, #lying counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
  
  variable_name <- paste("sitting_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$sitting, #sitting counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
  
  variable_name <- paste("standing_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$standing, #standing counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
  
  variable_name <- paste("not_visible_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$not_visible, #not_visible counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
}

```


# xbar chart

## timestep = 15min

```{r}
  # aggregate with the function
aggregate_by_day(frequency_position_15min_05_to_14_07_2022, time = "15min")
```

Plots :
```{r}
#Plot xbar charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = not_visible_byday_15min[5:10,],  #5-11 days = test phase
    confidence.level = 0.99,       #increase confidence level (default = 0.95)
    add.stats = FALSE)  +          #don't display center, std & number of groups
  scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```
With a calibration phase of 5 days, every measure is within the UCL/LCL thresholds.

## timestep = 30min

```{r}
  # aggregate with the function
aggregate_by_day(frequency_position_30min_8h_21h_05_to_14_07_2022, time = "30min")
```

Plots :
```{r}
#Plot xbar charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = lying_byday_30min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = sitting_byday_30min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = standing_byday_30min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = not_visible_byday_30min[5:10,],  #5-11 days = test phase
    confidence.level = 0.99,       #increase confidence level (default = 0.95)
    add.stats = FALSE)  +          #don't display center, std & number of groups
  scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```

## timestep = 1h

```{r}
  # aggregate with the function
aggregate_by_day(frequency_position_1h_8h_21h_05_to_14_07_2022, time = "1h")
```

Plots :
```{r}
#Plot xbar charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = lying_byday_1h[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = sitting_byday_1h[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = standing_byday_1h[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = not_visible_byday_1h[5:10,],  #5-11 days = test phase
    confidence.level = 0.99,       #increase confidence level (default = 0.95)
    add.stats = FALSE)  +          #don't display center, std & number of groups
  scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```

# R chart

```{r}
#Plot R charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = not_visible_byday_15min[5:10,])  #5-11 days = test phase
```
There are out-of-control data for points that are in the calibration period. This is weird, but not impossible. The UCL & LCL are created depending on the values of all the points in the calibration period. So the IC95% of a point is not created around this point only. It's supposed to be fix for every point, the only difference is that this IC is higher when we have less data for the daily observation. But a higer value doesn't mean a higher IC.

## S chart

```{r}
#Plot S charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = not_visible_byday_15min[5:10,])  #5-11 days = test phase
```

## p chart

```{r}
#Plot S charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "p",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = not_visible_byday_15min[5:10,])  #5-11 days = test phase
```






