---
title: "Shewhart indicator 1.3"
author: "Mathilda Alhamadah"
date: "2025-07-21"
output: html_document
---

# 0. Starter


```{r}
library(qcc)
library(jsonlite)
library(purrr)
library(curl)
library(dplyr)
library(lubridate)
library(tidyr)
library(ggplot2)
library(patchwork)
```


# 1. Load data

Load the data here :

```{r}
load("data_QCC_indicator1.3_reliable_15min_to_6h.Rdata")
```


## → But how to get this data ?


1st load or create the data from 05 to 14 of July with only reliable data & without anesthesia data :

```{r}
# Load the 05-14 of July data
load("reliable_data_8h_21h_05_to_14_07_2022.Rdata")
```

Then load the frequency_position function from file indicator_1 :

```{r}
# Frequency of postures lying/ sitting/ standing by timestep (chosen)

frequency_position <- function(data,
                               interval_seconds,
                               existing_data_percent) {
  data <- data %>% arrange(Date_Time) #sort by date
  
  start_time <- min(data$Date_Time)   #oldest frame
  end_time <- max(data$Date_Time)     #newest frame
  
  #Cut between these 2 frames depending on the time interval
  intervals <- seq(from = start_time, to = end_time, by = interval_seconds)
  
  
  df_counts <- data.frame(                       #create the new df
    start_time = intervals[-length(intervals)],  #drop the last time
    end_time = intervals[-1]                     #drop the first time
  )
  
  #Create the 4 posture variables
  df_counts <- df_counts %>%
    rowwise() %>%               #for each line
    mutate(
      lying = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 0, na.rm = TRUE),       #count lying
      standing = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 1, na.rm = TRUE),       #count standing
      sitting = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 2, na.rm = TRUE),       #count sitting
      not_visible = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 3, na.rm = TRUE)      #count not visible
    )
  
  #But keep it as numbers only if at least x% of data are not NA
  df_counts <- df_counts %>%
    #for those 4 columns
    mutate(across(c(sitting, standing, lying, not_visible),
                  #if less than x% of existing data
                  ~ if_else(sum(sitting, lying, standing, not_visible, na.rm = TRUE)/interval_seconds < (existing_data_percent / 100),
                            #then assign NA to each variable
                            NA,
                            #else : do nothing
                            .)))

  return(df_counts)
}
```

Then apply it to the data :

```{r}
# Compute the frequency of each posture 
frequency_position_15min_05_to_14_07_2022 <-
  frequency_position(data = reliable_data_8h_21h_05_to_14_07_2022, #data
                     interval_seconds = 900, #15min
                     existing_data_percent = 95)  #max 5% of NA data for 15-30min, max 50% for 1h & more
```

Then sum the sitting & standing occurences (vs lying & not visible) :

```{r}
# Sum the standing & sitting occurences
frequency_position_15min_05_to_14_07_2022_StandingSitting <- frequency_position_15min_05_to_14_07_2022 %>% 
  mutate(sitting_standing = sum(sitting, standing),
         lying_not_visible = sum(lying, not_visible)) #maybe useless but maybe not

rm(frequency_position_15min_05_to_14_07_2022)
```


Then we want to remove the data outside the 8h-21h range :

```{r}
#function
filter_8h_21h <- function(data, time_column){
  data <- data %>%
    filter(hour({{time_column}}) >= 8 & hour({{time_column}}) < 21)
  return(data)
}
```

```{r}
#apply function
frequency_position_15min_8h_21h_05_to_14_07_2022_StandingSitting <- filter_8h_21h(data = frequency_position_15min_05_to_14_07_2022_StandingSitting,
                                                            time_column = start_time)

rm(frequency_position_15min_05_to_14_07_2022_StandingSitting) #remove useless data
```

Now we need to remove again data of day 08/07 between 9h6m57 and 10h14m09s. Since they have already been removed in the original "reliable_data...", their value is 0 for each variable. But we don't want to have zeros if we removed the data, we want to have NAs. So we are just going to assign "NA" to these data so that it won't mess up because of missing lines :

```{r}
frequency_position_15min_8h_21h_05_to_14_07_2022_StandingSitting <- frequency_position_15min_8h_21h_05_to_14_07_2022_StandingSitting %>%
  mutate(
      #Define what's in the time we want to drop
    in_interval = end_time >= as.POSIXct("2022-07-08 09:06:57") & start_time <= as.POSIXct("2022-07-08 10:14:09"),
      #If in the time : NA, else : normal value
    sitting_standing = if_else(in_interval, NA, sitting_standing),
    lying_not_visible = if_else(in_interval, NA, lying_not_visible)
  ) %>%
  select(-in_interval)  #Remove temporary variable

```

Warning : this is the most restrictive removal we can do. For example if the timestep is 2hours it will make the whole line go to NA. But if we want to be less restrictive, we just have to switch end_time and start_time : it will remove only lines that have both end_time and start_time in the interval. Whereas here, we remove lines if they have at least one time in the interval. I know it sounds weird but it works, the difference is about overlap of intervals : does it have to be partial or total to be NA ? Most restrictive (our case) = partial.

Now we want to create a day variable to aggregate by day :

```{r}
frequency_position_15min_8h_21h_05_to_14_07_2022_StandingSitting <- frequency_position_15min_8h_21h_05_to_14_07_2022_StandingSitting %>%
  mutate(day = as.Date(start_time))
```

Now we're all done ! Do that for every timestep you want to try. You can still load the final data here :

```{r}
load("data_QCC_indicator1.3_reliable_15min_to_6h.Rdata")
```


# 2. Aggregate by day

```{r}
#Aggregate by day with QCC function

aggregate_by_day_1.3 <- function(frequency_position_data, time) {
  
  variable_name <- paste("standing_sitting_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$standing_sitting, #lying counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
  
  variable_name <- paste("lying_not_visible_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$lying_not_visible, #sitting counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
}

```


```{r}
# ça marche : 
qcc.groups(data = frequency_position_15min_8h_21h_05_to_14_07_2022_StandingSitting$sitting_standing,
           sample = frequency_position_15min_8h_21h_05_to_14_07_2022_StandingSitting$day)

#pourtant ça marche pas : 

# Apply function
aggregate_by_day_1.3(frequency_position_15min_8h_21h_05_to_14_07_2022_StandingSitting, time = "15min")
```


# 3. Xbar chart