---
title: "Shewhart indicator 1.1"
author: "Mathilda Alhamadah"
date: "2025-07-04"
output: html_document
---
# 0. Starter

## a) What do we do

We're going to run the Shewhart algorithm using the QCC package on our data from 04 to 14th of July, 2022.
Shewhart because it's the easiest to begin & QCC because it doesn't use a real time metric so it's useful for our incomplete data with a "false" time metric (aggregating days but skipping the 21h-8h part). Also QCC is practical because of NA management : accepted (unless it's a whole day).

## b) Hypothesis

Data = realizations of iid random variable (VA), follows a normal distribution, no trend or cyclicity in data.
Possible with non normal data (ref : Clement, 2017) but not very clear about that.

## c) Pros & cons

*Pros :*
Simple to implement & interpret. Allows a quick detection of sudden & important changes in the process.
No need to transform data : we directly plot the process. We only build upper control limit (UCL) & lower control limit (LCL)

*Cons :*
Not very sensitive to small changes.


```{r}
library(qcc)
library(jsonlite)
library(purrr)
library(curl)
library(dplyr)
library(lubridate)
library(tidyr)
library(ggplot2)
library(patchwork)
```


# 1. Load data

```{r}
load("data_QCC_indicator1.1_reliable_15min_to_6h.Rdata")
```

## → How to get this data ?

Start from the data directly obtained with YOLO (see doc Read_Json_files) :
* But without anesthesia data (= data of the 05/07 + data of the 08/07 only between 9h6m57 and 10h14m09s)
* And without non reliable data (= data with a confidence < 1/3 ~ 0.34, and if > 2 predictions data with a confidence_gap < 0.2 between the 2 most reliable predictions)
* And without data outside 8h-21h

```{r}
#You can load it here :
load("reliable_data_8h_21h_05_to_14_07_2022.Rdata")
```

Then run the whole "frequency_position" function from file indicator_1 :

```{r}
# Frequency of postures lying/ sitting/ standing by timestep (chosen)

frequency_position <- function(data,
                               interval_seconds,
                               existing_data_percent) {
  data <- data %>% arrange(Date_Time) #sort by date
  
  start_time <- min(data$Date_Time)   #oldest frame
  end_time <- max(data$Date_Time)     #newest frame
  
  #Cut between these 2 frames depending on the time interval
  intervals <- seq(from = start_time, to = end_time, by = interval_seconds)
  
  
  df_counts <- data.frame(                       #create the new df
    start_time = intervals[-length(intervals)],  #drop the last time
    end_time = intervals[-1]                     #drop the first time
  )
  
  #Create the 4 posture variables
  df_counts <- df_counts %>%
    rowwise() %>%               #for each line
    mutate(
      lying = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 0, na.rm = TRUE),       #count lying
      standing = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 1, na.rm = TRUE),       #count standing
      sitting = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 2, na.rm = TRUE),       #count sitting
      not_visible = sum(data$Date_Time >= start_time & data$Date_Time < end_time & data$class_id == 3, na.rm = TRUE)      #count not visible
    )
  
  #But keep it as numbers only if at least x% of data are not NA
  df_counts <- df_counts %>%
    #for those 4 columns
    mutate(across(c(sitting, standing, lying, not_visible),
                  #if less than x% of existing data
                  ~ if_else(sum(sitting, lying, standing, not_visible, na.rm = TRUE)/interval_seconds < (existing_data_percent / 100),
                            #then assign NA to each variable
                            NA,
                            #else : do nothing
                            .)))

  return(df_counts)
}
```


Now for each timestep you want, run this (example with 15min) :

```{r}
#interval_seconds = the timestep you want in seconds. Here : 15min*60 = 900 seconds.
frequency_position_15min_05_to_14_07_2022 <-
  frequency_position(data = reliable_data_8h_21h_05_to_14_07_2022, #data
                     interval_seconds = 900, #15min
                     existing_data_percent = 95)  #max 5% NA for 15-30min, max 50% for 1h & more
```

But this made us have lines outside the 8h-21h gap again. We want to remove them :

```{r}
#function
filter_8h_21h <- function(data, time_column){
  data <- data %>%
    filter(hour({{time_column}}) >= 8 & hour({{time_column}}) < 21)
  return(data)
}

#apply function
frequency_position_15min_8h_21h_05_to_14_07_2022 <- filter_8h_21h(data = frequency_position_15min_05_to_14_07_2022,
                                                            time_column = start_time)

rm(frequency_position_15min_05_to_14_07_2022) #remove useless data
```

Now we need to remove again data of day 08/07 between 9h6m57 and 10h14m09s. Since they have already been removed in the original "reliable_data...", their value is 0 for each variable. But we don't want to have zeros if we removed the data, we want to have NAs. So we are just going to assign "NA" to these data so that it won't mess up because of missing lines :

```{r}
frequency_position_15min_8h_21h_05_to_14_07_2022 <- frequency_position_15min_8h_21h_05_to_14_07_2022 %>%
  mutate(
      #Define what's in the time we want to drop
    in_interval = end_time >= as.POSIXct("2022-07-08 09:06:57") & start_time <= as.POSIXct("2022-07-08 10:14:09"),
      #If in the time : NA, else : normal value
    sitting = if_else(in_interval, NA, sitting),
    standing = if_else(in_interval, NA, standing),
    lying = if_else(in_interval, NA, lying),
    not_visible = if_else(in_interval, NA, not_visible)
  ) %>%
  select(-in_interval)  #Remove temporary variable

```

Warning : this is the most restrictive removal we can do. For example if the timestep is 2hours it will make the whole line go to NA. But if we want to be less restrictive, we just have to switch end_time and start_time : it will remove only lines that have both end_time and start_time in the interval. Whereas here, we remove lines if they have at least one time in the interval. I know it sounds weird but it works, the difference is about overlap of intervals : does it have to be partial or total to be NA ? Most restrictive (our case) = partial.

Now we want to create a day variable to aggregate by day :

```{r}
frequency_position_15min_8h_21h_05_to_14_07_2022 <- frequency_position_15min_8h_21h_05_to_14_07_2022 %>%
  mutate(day = as.Date(start_time))
```

Now we're all done ! Do that for every timestep you want to try. You can still load the final data here :

```{r}
load("data_QCC_indicator1_reliable_15min_to_6h.Rdata")
```


# 2. Aggregate by day

```{r}
#Aggregate by day with QCC function

aggregate_by_day_1.1 <- function(frequency_position_data, time) {
  
  variable_name <- paste("lying_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$lying, #lying counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
  
  variable_name <- paste("sitting_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$sitting, #sitting counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
  
  variable_name <- paste("standing_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$standing, #standing counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
  
  variable_name <- paste("not_visible_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$not_visible, #not_visible counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
}

```


```{r}
# Apply function
# 
#   #15min
# aggregate_by_day_1.1(frequency_position_15min_8h_21h_05_to_14_07_2022, time = "15min")
# 
#   #30min
# aggregate_by_day_1.1(frequency_position_30min_8h_21h_05_to_14_07_2022, time = "30min")
# 
# 
#   #1h
# aggregate_by_day_1.1(frequency_position_1h_8h_21h_05_to_14_07_2022, time = "1h")
# 
# 
#   #2h
# aggregate_by_day_1.1(frequency_position_2h_8h_21h_05_to_14_07_2022, time = "2h")
# 
# 
#   #4h
# aggregate_by_day_1.1(frequency_position_4h_8h_21h_05_to_14_07_2022, time = "4h")
# 
# 
#   #6h
# aggregate_by_day_1.1(frequency_position_6h_8h_21h_05_to_14_07_2022, time = "6h")

```

# 3. Xbar chart

## a) timestep = 15min

Data :
```{r}
  #15min
aggregate_by_day_1.1(frequency_position_15min_8h_21h_05_to_14_07_2022, time = "15min")
```


Plots :
```{r}
#Plot xbar charts for every posture 


  #lying, timesteps = 15min, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 15min, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 15min, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 15min, 1point = 1day, with more control of the outputs
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = not_visible_byday_15min[5:10,],  #5-11 days = test phase
    confidence.level = 0.99,       #increase confidence level (default = 0.95)
    add.stats = FALSE)  +          #don't display center, std & number of groups
  scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```
With a calibration phase of 5 days, every measure is within the UCL/LCL thresholds.

## b) timestep = 30min

Data :
```{r}
  #30min
aggregate_by_day_1.1(frequency_position_30min_8h_21h_05_to_14_07_2022, time = "30min")
```

Plots :
```{r}
#Plot xbar charts for every posture 

  #lying, timesteps = 30min, 1point = 1day
qcc(data = lying_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = lying_byday_30min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 30min, 1point = 1day
qcc(data = sitting_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = sitting_byday_30min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 30min, 1point = 1day
qcc(data = standing_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = standing_byday_30min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 30min, 1point = 1day
qcc(data = not_visible_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = not_visible_byday_30min[5:10,],  #5-11 days = test phase
    confidence.level = 0.99,       #increase confidence level (default = 0.95)
    add.stats = FALSE)  +          #don't display center, std & number of groups
  scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```

## c) timestep = 1h

```{r}
  #1h
aggregate_by_day_1.1(frequency_position_1h_8h_21h_05_to_14_07_2022, time = "1h")
```

Plots :
```{r}
#Plot xbar charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = lying_byday_1h[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = sitting_byday_1h[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = standing_byday_1h[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = not_visible_byday_1h[5:10,],  #5-11 days = test phase
    confidence.level = 0.99,       #increase confidence level (default = 0.95)
    add.stats = FALSE)  +          #don't display center, std & number of groups
  scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```

## c) timestep = 2h

```{r}
  #2h
aggregate_by_day_1.1(frequency_position_2h_8h_21h_05_to_14_07_2022, time = "2h")
```

Plots :
```{r}
#Plot xbar charts for every posture 

  #lying, timesteps = 2h, 1point = 1day
qcc(data = lying_byday_2h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = lying_byday_2h[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 2h, 1point = 1day
qcc(data = sitting_byday_2h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = sitting_byday_2h[5:10,]) #5-11 days = test phase


  #standing, timesteps = 2h, 1point = 1day
qcc(data = standing_byday_2h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = standing_byday_2h[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 2h, 1point = 1day
qcc(data = not_visible_byday_2h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = not_visible_byday_2h[5:10,],  #5-11 days = test phase
    confidence.level = 0.99,       #increase confidence level (default = 0.95)
    add.stats = FALSE)  +          #don't display center, std & number of groups
  scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```


## c) timestep = 4h

```{r}
  #4h
aggregate_by_day_1.1(frequency_position_4h_8h_21h_05_to_14_07_2022, time = "4h")
```

Plots :
```{r}
#Plot xbar charts for every posture 

  #lying, timesteps = 4h, 1point = 1day
qcc(data = lying_byday_4h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = lying_byday_4h[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 4h, 1point = 1day
qcc(data = sitting_byday_4h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = sitting_byday_4h[5:10,]) #5-11 days = test phase


  #standing, timesteps = 4h, 1point = 1day
qcc(data = standing_byday_4h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = standing_byday_4h[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 4h, 1point = 1day
qcc(data = not_visible_byday_4h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = not_visible_byday_4h[5:10,],  #5-11 days = test phase
    confidence.level = 0.99,       #increase confidence level (default = 0.95)
    add.stats = FALSE)  +          #don't display center, std & number of groups
  scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```


## c) timestep = 6h

This part does not work because some days only have 1 group of 6 hours filled, and there must be at least 2 groups for QCC (otherwise no confidence intervals).

```{r}
  #6h
aggregate_by_day_1.1(frequency_position_6h_8h_21h_05_to_14_07_2022, time = "6h")
```

Plots (doesn't work because no data enough) :
```{r}
# #Plot xbar charts for every posture 
# 
#   #lying, timesteps = 6h, 1point = 1day
# qcc(data = lying_byday_6h[1:4,], #5 first days = calibration
#     type = "xbar",               #chart type
#     newdata = lying_byday_6h[5:10,])  #5-11 days = test phase
# 
# 
#   #sitting, timesteps = 6h, 1point = 1day
# qcc(data = sitting_byday_6h[1:4,], #5 first days = calibration
#     type = "xbar",               #chart type
#     newdata = sitting_byday_6h[5:10,]) #5-11 days = test phase
# 
# 
#   #standing, timesteps = 6h, 1point = 1day
# qcc(data = standing_byday_6h[1:4,], #5 first days = calibration
#     type = "xbar",               #chart type
#     newdata = standing_byday_6h[5:10,]) #5-11 days = test phase
# 
# 
#   #not visible, timesteps = 6h, 1point = 1day
# qcc(data = not_visible_byday_6h[1:4,], #5 first days = calibration
#     type = "xbar",               #chart type
#     newdata = not_visible_byday_6h[5:10,],  #5-11 days = test phase
#     confidence.level = 0.99,       #increase confidence level (default = 0.95)
#     add.stats = FALSE)  +          #don't display center, std & number of groups
#   scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```


# 4. R chart

```{r}
#Plot R charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = not_visible_byday_15min[5:10,])  #5-11 days = test phase
```
There are out-of-control data for points that are in the calibration period. This is weird, but not impossible. The UCL & LCL are created depending on the values of all the points in the calibration period. So the IC95% of a point is not created around this point only. It's supposed to be fix for every point, the only difference is that this IC is higher when we have less data for the daily observation. But a higer value doesn't mean a higher IC.

# 5. S chart

```{r}
#Plot S charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = not_visible_byday_15min[5:10,])  #5-11 days = test phase
```

# 6. p chart

```{r}
#Plot S charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "p",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = not_visible_byday_15min[5:10,])  #5-11 days = test phase
```




