---
title: "Shewhart with QCC"
author: "Mathilda Alhamadah"
date: "2025-07-04"
output: html_document
---
# Starter

## What do we do

We're going to run the Shewhart algorithm using the QCC package on our data from 04 to 14th of July, 2022.
Shewhart because it's the easiest to begin & QCC because it doesn't use a real time metric so it's useful for our incomplete data with a "false" time metric (aggregating days but skipping the 21h-8h part). Also QCC is practical because of NA management : accepted (unless it's a whole day).

## Hypothesis

Data = realizations of iid random variable (VA), follows a normal distribution, no trend or cyclicity in data.
Possible with non normal data (ref : Clement, 2017) but not very clear about that.

## Pros

Simple to implement & interpret. Allows a quick detection of sudden & important changes in the process.
No need to transform data : we directly plot the process. We only build upper control limit (UCL) & lower control limit (LCL)

## Cons

Not very sensitive to small changes.


```{r}
library(qcc)
library(jsonlite)
library(purrr)
library(curl)
library(dplyr)
library(lubridate)
library(tidyr)
library(ggplot2)
library(patchwork)
```

## How to change timestep

2 chunks to change timestep (load frequency_position data with the right timestep & remove data outside 8h-21h and then add a day variable

```{r}
# #function to keep only data between 8h & 21h
# filter_8h_21h <- function(data, time_column){
#   data <- data %>%
#     filter(hour({{time_column}}) >= 8 & hour({{time_column}}) < 21)
#   return(data)
# }
```

```{r}
# #keep only data between 8h & 21h
# frequency_position_30min_8h_21h_04_to_14_07_2022 <- filter_8h_21h(data = frequency_position_30min_04_to_14_07_2022,
#                                                             time_column = start_time)
# 
# #create a day variable to aggregate by day
# frequency_position_30min_8h_21h_04_to_14_07_2022 <- frequency_position_30min_8h_21h_04_to_14_07_2022 %>%
#   mutate(day = as.Date(start_time))
```

## Remove anesthesia data

When the fox is absent, we don't want it to be as if he was not visible. When he wakes up from anesthesia, we don't want it to be as if he was always lying in free will. We have to delete the 1st day because it was almost only anesthesia or a wake up from anesthesia.


```{r}
# #load data
# load("data_QCC_indicator1_15min_04_to_14_07_2022.Rdata")
# 
# #remove day 04/07/2022
# frequency_position_30min_05_to_14_07_2022 <- frequency_position_30min_04_to_14_07_2022 %>% 
#   filter(date(start_time) != "2022-07-04")
# 
# frequency_position_30min_8h_21h_05_to_14_07_2022 <- frequency_position_30min_8h_21h_04_to_14_07_2022 %>% 
#   filter(date(start_time) != "2022-07-04")
# 
# rm(frequency_position_30min_04_to_14_07_2022, frequency_position_30min_8h_21h_04_to_14_07_2022)

```


```{r}
#Aggregate by day with QCC function

  # function

aggregate_by_day <- function(frequency_position_data, time) {
  
  variable_name <- paste("lying_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$lying, #lying counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
  
  variable_name <- paste("sitting_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$sitting, #sitting counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
  
  variable_name <- paste("standing_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$standing, #standing counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
  
  variable_name <- paste("not_visible_byday", time, sep = "_")
  assign(variable_name, qcc.groups(data = frequency_position_data$not_visible, #not_visible counts only
                                   sample = frequency_position_data$day), 
         envir = .GlobalEnv)
}

```


# xbar chart

## timestep = 15min

```{r}
  # aggregate with the function
aggregate_by_day(frequency_position_15min_8h_21h_05_to_14_07_2022, time = "15min")
```

Plots :
```{r}
#Plot xbar charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = not_visible_byday_15min[5:10,],  #5-11 days = test phase
    confidence.level = 0.99,       #increase confidence level (default = 0.95)
    add.stats = FALSE)  +          #don't display center, std & number of groups
  scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```
With a calibration phase of 5 days, every measure is within the UCL/LCL thresholds.

## timestep = 30min

```{r}
  # aggregate with the function
aggregate_by_day(frequency_position_30min_8h_21h_05_to_14_07_2022, time = "30min")
```

Plots :
```{r}
#Plot xbar charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = lying_byday_30min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = sitting_byday_30min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = standing_byday_30min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_30min[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = not_visible_byday_30min[5:10,],  #5-11 days = test phase
    confidence.level = 0.99,       #increase confidence level (default = 0.95)
    add.stats = FALSE)  +          #don't display center, std & number of groups
  scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```

## timestep = 1h

```{r}
  # aggregate with the function
aggregate_by_day(frequency_position_1h_8h_21h_05_to_14_07_2022, time = "1h")
```

Plots :
```{r}
#Plot xbar charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = lying_byday_1h[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = sitting_byday_1h[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = standing_byday_1h[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_1h[1:4,], #5 first days = calibration
    type = "xbar",               #chart type
    newdata = not_visible_byday_1h[5:10,],  #5-11 days = test phase
    confidence.level = 0.99,       #increase confidence level (default = 0.95)
    add.stats = FALSE)  +          #don't display center, std & number of groups
  scale_x_date(date_breaks = "3 days", date_labels = "%d-%b") #none of these commands work
```

# R chart

```{r}
#Plot R charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "R",               #chart type
    newdata = not_visible_byday_15min[5:10,])  #5-11 days = test phase
```
There are out-of-control data for points that are in the calibration period. This is weird, but not impossible. The UCL & LCL are created depending on the values of all the points in the calibration period. So the IC95% of a point is not created around this point only. It's supposed to be fix for every point, the only difference is that this IC is higher when we have less data for the daily observation. But a higer value doesn't mean a higher IC.

## S chart

```{r}
#Plot S charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = not_visible_byday_15min[5:10,])  #5-11 days = test phase
```

## p chart

```{r}
#Plot S charts for every posture 

  #lying, timesteps = 1h, 1point = 1day
qcc(data = lying_byday_15min[1:4,], #5 first days = calibration
    type = "p",               #chart type
    newdata = lying_byday_15min[5:10,])  #5-11 days = test phase


  #sitting, timesteps = 1h, 1point = 1day
qcc(data = sitting_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = sitting_byday_15min[5:10,]) #5-11 days = test phase


  #standing, timesteps = 1h, 1point = 1day
qcc(data = standing_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = standing_byday_15min[5:10,]) #5-11 days = test phase


  #not visible, timesteps = 1h, 1point = 1day
qcc(data = not_visible_byday_15min[1:4,], #5 first days = calibration
    type = "S",               #chart type
    newdata = not_visible_byday_15min[5:10,])  #5-11 days = test phase
```






